\documentclass[]{deedy-resume-openfont}
\begin{document}
\title{Resume}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     October 7,2017.  will change over the next few days
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Keion}{Bisland}{
\location{\qquad \qquad \qquad \qquad \quad \qquad \qquad  }
\href{mailto:kbisland@wpi.edu}{kbisland@wpi.edu} | 508-654-1802 | \href{https://users.wpi.edu/~kbisland/}{Website: wpi.edu/\textasciitilde kbisland/} | \href{https://github.com/keionbis}{Github: keionbis}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{Worcester Polytechnic\newline Institute}
\descript{Bachelors degree in Robotics Engineering July 2019}
\location{June 2019 | Worcester Ma, United States}
\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Coursework}
\subsection{Robotics Engineering}
Introduction to Robotics\\
Unified Robotics I\\
Unified Robotics II\\
Unified Robotics III\\
Unified Robotics IV\\
Social Implications of Robotics\\
Control Engineering I
\sectionsep
\subsection{Computer Science}
System Programming \\
Object Oriented Design Concepts\\
Software Engineering\\
Human Computer Interaction
\sectionsep
\subsection{Electrical Engineering}
Introduction to Electrical Engineering\\
Embedded Computing in Engineering Design
\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Skills}
OSHA-10 certification\\
Fluent in multiple programming languages\\
Competent with Mac OS, Linux and Windows\\
PCB design experience\\
Solidworks experience\\
Fusion 360 CAD/CAM experience\\
3D Printing\\
CNC Machining
\sectionsep
\subsection{Fluent Languages}
English\\
Spanish
\sectionsep
\subsection{Coding Languages}
C\\
C++(including embed C++)\\
Java\\
Python\\
Pascal\\
Matlab\\
Latex
\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}

\descript{6-DOF Robotic Arm}
\vspace{\topsep}
\begin{tightemize} 
\item Designed and 3D printed a modular 6 degree of freedom robotic arm.
\item Designed a custom breakout PCB for the Nucleo 144 micro controller development board.
\item Coded a control system for the arm using encoder feedback for each motor.
\end{tightemize}

\descript{Electric Longboard}
\begin{tightemize} 
\item CAD and CAM of a custom adjustable motor mount
\item Manufactured a multi-layer composite deck
\item Designed and manufactured a custom battery pack and balance charging circuit
\item Designed and manufactured a custom controller including feedback from the motors to determine direction and speed.
\end{tightemize}

\descript{Robotics Course}
\begin{tightemize} 
\item Designed a sub \$50 educational robotics kit. 
\item Adapted WPIs intro to robotics course for the use with this kit for use in developing countries
\item Ran trials of our course in local high schools.
\end{tightemize}

\descript{Assisted in the development of a Robotic arm for Unified Robotics III}
\begin{tightemize} 
\item Designed a mother and daughter board for the feedback system of the arm.
\item Assembled, tested and modified the preliminary revisions of the arm.
\item Assembled and tested mother and daughter boards including SMD components.
\item Tested and developed firmware and matlab interfacing.
\end{tightemize}

\descript{Designed and Manufactured a 3 DOF end effector}
\begin{tightemize} 
\item Designed a 3D printable 3 edgree of freedom wrist end-effector for the unified Robotics III Robotic arm.
\item Printed, tested and modified the wrist mechanism.
\item Programmed the control structure for the wrist.
\end{tightemize}

\descript{Software Engineering: Recreated the alcohol registry process for the TTB agency}
\begin{tightemize} 
\item Designed a front end interface for user to search for alcohol submissions.
\item Designed an interface for companies to submit and update alcohol labels.
\item Restructured the current TTB database.
\item Added failsafe checks in order to prevent incorrect/ invalid data from being entered.
\end{tightemize}
\end{minipage} 
%\sectionsep



\hfill
\begin{minipage}[t]{0.33\textwidth} 
%page 2 first col
\subsection{Conferences}
MS4SSA Multi-lingual conference held at WPI\\
Robotia AUVSI conference 2017 \\
\sectionsep
\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 
\descript{3D Printed Quadruped}
\begin{tightemize} 
\item Designed custom Motherboard to connect Raspberry Pi Zero W, a Teensy 3.5, a 6 DOF IMU and up to 20 Servos. 
\item Coded communication protocol between Raspberry Pi and Teensy 3.5.
\item Coded with partner on the overall control structure for the robot
\end{tightemize}
\descript{LED Matrix}
\begin{tightemize} 
\item Designed and built a 30x30 LED matrix using individually addressable leds.
\item Created custom animations and displays using the raspberry pi 3.
\item Using the ESP32 micro-controller, we replaced the raspberry pi and created an internet accessible version.
\item integrate the amazon echo for control.
\end{tightemize}
\section{Positions of Responsibility}
\runsubsection{WPI Collab Lab (On campus maker space)}
\descript{| Lab Monitor}
\location{2016- 2019}
\vspace{\topsep}
\runsubsection{WPI Washburn Shops (On Campus machine shop)}
\descript{| Lab Monitor}
\location{2017- 2019}
\runsubsection{Unified Robotics I \& II}
\descript{| Student Assistant}
\location{2017- 2019}
\newpage
\runsubsection{Software Engineering}
\descript{| Lead Software Engineer}
 \location{2017- 2019}

%\sectionsep
\end{minipage}


\end{document}  \documentclass[]{article}